---
title: "Functional Integrity"
author: "Michael Di Girolamo"
date: "5/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#setting up data
```{r}
setwd("C:/Users/mrdig/Desktop/SAIS/Food Systems/Biosphere Integrity")
data <- read.csv("Apex2021_FullTable_GAUL.csv",sep = ",",header = TRUE)
View(data)
data <- subset(data,select = c(ADM0_NAME, Integ1km10))
View(data)
```
#setting up map
#install package for rworldmap is useful to include in case the user does not yet have this package
```{r}
install.packages("rworldmap")
library(rworldmap)
mapworld <- joinCountryData2Map(data
                           , joinCode = "NAME"
                           , nameJoinColumn = "ADM0_NAME")

```
#plotting the map
#map_inte = integrity map name
#par code = formatting code that sets up axes - always copy it
#thing to note - while it's good to copy this section, always change the parts next to nameColumnToPlot, mapTitle, and anywhere with the name of the map in it
```{r}
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
map_inte <- mapCountryData(mapworld, nameColumnToPlot="Integ1km10",mapTitle = "Functional Integrity by Country", colourPalette = c("#f7fcf0","#e0f3db","#ccebc5","#a8ddb5","#7bccc4","#4eb3d3","#2b8cbe","#0868ac","#084081"),oceanCol = "gray",missingCountryCol = 'white',addLegend = FALSE)
do.call( addMapLegend, c( map_inte
                        , legendLabels="all"
                        , legendWidth=0.5
                        ))
```
