---
title: "Households with significant income from agriculture"
date: "May 25, 2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## 

"Created April 29, 2022"

## 

"Marissa Silverberg"

## 

"WG 3 Livelihoods & Equity"

## 

"Income and Poverty"

## 

The data being used is from FAO 
RuLIS: <https://www.fao.org/in-action/rural-livelihoods-dataset-rulis>, Eurostat: <https://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=lfsa_egan22d&lang=en>, and
ILO: <https://ilostat.ilo.org/data/> and the specific indicator is: EMP_TEMP_SEX_EC2_NB_A.


```{r}
library(rworldmap)
library(sf)
library(plyr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyverse)
```

```{r}
worldbank <- read_csv("~/Desktop/worldbank.csv")
fao <- read_csv("~/Desktop/FAOAgIncome.csv")
euro <- read_csv("~/Desktop/EUROSTATAgIncome.csv")
ilo <- read_csv("~/Desktop/ILOSTATAgIncome.csv")



ilo <- ilo %>% select(country,Year,Value)
fao <- fao %>% select(Country,Year,Thousands)
euro <- euro %>% select(Year,Value)


ilo <- na.omit(ilo)
fao <- na.omit(fao)
euro <- na.omit(euro)


merged_line <- left_join(ilo,fao,by = c("country" = "Country", "Year" = "Year" ,"Value" = "Thousands"))
View(merged_line)                         

str(merged_line)
```


```{r}
merged_line <- merged_line %>% filter(between(Year, 2012,2022))

library(plotly)
p <- ggplot(data=merged_line,
            aes(x=Year, y=Value, colour=country)) +
 geom_line()
ggplotly(p)
```


```{r}
map_world <- map_data("world")
ggplot(map_world, aes(x = long, y = lat, group = group)) +
 geom_polygon(fill="lightgray", colour = "white")


ilo_1 <- ilo %>% filter(Year == 2019)
fao_1 <- fao %>% filter(Year == 2019)
euro_1 <- euro %>% filter(Year == 2019)

euro_1$Value <- as.numeric(euro_1$Value)
euro_1 <- na.omit(euro_1)

merged_map_1 <- left_join(ilo_1,fao_1,by = c("country" = "Country", "Year" = "Year" ,"Value" = "Thousands"))
merged_map_2 <- left_join(merged_map_1,euro_1,by = c("Year" = "Year" ,"Value" = "Value"))

View(merged_map_2)
View(map_world)


merged_map_2 <- aggregate(Value ~ country, data=merged_map_2, FUN=sum)
```


```{r}
map_world <- map_world[,-6]
map_final <- left_join(map_world,merged_map_2,by = c("region" = "country"))
map_final <- na.omit(map_final)
View(map_final)

view(map_world)
```

```{r}
mapworld <- joinCountryData2Map(merged_map_2, joinCode = "NAME", nameJoinColumn = "country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(mapworld, nameColumnToPlot="Value" , mapTitle = "Households with Significant Income from Agriculture (thousands), 2019", colourPalette = c("#e0f3db","#ccebc5","#a8ddb5","#7bccc4","#4eb3d3","#2b8cbe","#0868ac","#084081"), oceanCol = "gray", missingCountryCol = 'white')
```

```

```{r}
WorldMap_AgIncome <- joinCountryData2Map(map_world, 
                                        joinCode = "NAME", 
                                        nameJoinColumn = "region")
par(mai=c(0,0,0.2,0), xaxs="i",yaxs="i")
mapCountryData(WorldMap_AgIncome, 
               nameColumnToPlot = "largest", 
               mapTitle = "% Adequacy of benefits from social protection and labor programs, 2012-2019", 
               colourPalette = c("#e0f3db",
                                 "#ccebc5",
                                 "#a8ddb5",
                                 "#7bccc4",
                                 "#4eb3d3",
                                 "#2b8cbe",
                                 "#0868ac" #,
                                 #"#084081"
                                 ), 
               oceanCol = "gray", 
               missingCountryCol = 'white')
```


```{r}
view(WorldMap_AgIncome)

ggplot(map_final, aes(map_id = region, fill = Value))+
 geom_map(map = map_final,  color = "white")+
 expand_limits(x = map_final$long, y = map_final$lat)+
 scale_fill_viridis_c(option = "C")
```


```{r}

```

```{r}
# Create dataframe across FAO/EURO/ILO

#FAO_df <- FAO %>%
 # select("wb_region", "2010", "2011", "2012", 
         "2013", "2014", "2015", "2016", "2017",
         "2018", "2019")





EURO_df <- EURO %>%
  select("ref_area", "2010", "2011", "2012", 
         "2013", "2014", "2015", "2016", "2017",
         "2018", "2019")

ILO_df <- spcoverage %>%
  select("wb_region", "2010", "2011", "2012", 
         "2013", "2014", "2015", "2016", "2017",
         "2018", "2019")
merge 

df1 <- data.frame(FAO, EURO, ILO)
# Print top rows
head(df1)

target <- c("Households with significant income from agriculture")
index <- FAO$seriesname %in% target
df <- data[index, ]
glimpse(df)
```

```{r}
unique(df$Year)
```


```{r}
world <- map_data("world") # set up world map
```


```{r}

data(wrld_simpl)
#wrld_simpl <- st_as_sf(wrld_simpl)
#glimpse(wrld_simpl)
```





```{r}
countries <- unique(df$country)
unique(worldbank$Country)
candidates_countries  <- worldbank$Country %in% countries


df_countries <- worldbank[candidates_countries, ]
df_countries
```



```{r}
names(df)[names(df) == 'country'] <- 'Country'
df
```



```{r}

merge_df <- join(df, df_countries,
     type = "inner")
```


```{r}
glimpse(merge_df)
```

```{r}
unique(merge_df$ISO3)
```


```{r}
wrld_simpl$ISO3 <- as.character(wrld_simpl$ISO3)
unique(wrld_simpl$ISO3)
```

```{r}
names(merge_df)[names(merge_df) == 'country_code'] <- 'ISO3'
```

```{r}
#wrld_simpl$ISO3 <- unlist(wrld_simpl$ISO3)
#merge_df$ISO3 <- unlist(merge_df$ISO3)
```



```{r}
names(merge_df)[names(merge_df) == 'value'] <- 'Households with significant income from agriculture'
```


```{r}

#merge_df$Year <-year(merge_df$Year)
#countries <-  merge(countries, df, by.x = "ISO3", by.y = "Country.Code")
joinData <- joinCountryData2Map( merge_df,
                                 joinCode = "NAME",
                                 nameJoinColumn = "Country")
```


```{r}
theMap <- mapCountryData( joinData, nameColumnToPlot="Households with significant income from agriculture", addLegend=FALSE )
do.call( addMapLegend, c(theMap, legendWidth=1, legendMar = 2))
```



```{r}
par(mai = c(0, 0, 0.2, 0), xaxs = "i", yaxs = "i")
mapCountryData(joinData, mapTitle = "Households with significant income from agriculture", nameColumnToPlot = "Households with significant income from agriculture", catMethod = "categorical",colourPalette = "diverging", numCats = 5)
```



```{r}

# Summarize medianGdpPercap within each wb_region within each year: by_year_continent
by_year_continent <- merge_df %>%
group_by(wb_region, Year)

# Plot the change in  in each Households with significant income from agriculture region over time
ggplot(by_year_continent, aes(x = Year, y = merge_df$`Households with significant income from agriculture`, color = wb_region)) +
geom_line()+
expand_limits(y = 0)
```


```{r}
by_continent <- merge_df %>%
  group_by(wb_region)
# Create a bar plot showing medianGdp by continent

ggplot(by_continent, aes(x = wb_region, y = merge_df$`Households with significant income from agriculture`)) + geom_col()
```
```{r}
par(mai = c(0, 0, 0.2, 0), xaxs = "i", yaxs = "i")
MAP<- mapCountryData(joinData, mapTitle = "Households with significant income from agriculture", nameColumnToPlot = "Households with significant income from agriculture", catMethod = "categorical",colourPalette = "diverging", numCats = 5)
```



```{r}
library(viridis)
my_color <- c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00') 

pci_bar <- merge_df %>% 
  ggplot(aes(x = reorder(merge_df$Country, merge_df$`Households with significant income from agriculture`), y = merge_df$`Households with significant income from agriculture`, fill= merge_df$wb_region )) +
  geom_col(width = 0.7)+
  theme_bw()+
  xlab(NULL)+
  ylab("Households with significant income from agriculture")+
  scale_y_continuous(expand = c(0,0), limit = c(0,80))+ 
  labs (title = "Households with significant income from agriculture, 2020",
        caption = "https://www.fao.org/in-action/rural-livelihoods-dataset-rulis/data-application/data/by-indicator/en") +
  scale_fill_viridis(discrete = TRUE) +
  theme(legend.title = element_blank(),
        axis.ticks = element_blank(),
        plot.caption = element_text(face = "italic"))+
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())+ 
  geom_text(aes(label = merge_df$`Households with significant income from agriculture`), size= 2.5, hjust = -0.2)+
  coord_flip()

pci_bar
```


```{r}
#cowplot::plot_grid(MAP, NULL, pci_bar, ncol = 3,rel_widths = c(1, 0.3, 1.5))
#ggpubr::ggarrange(MAP, pci_bar, widths = c(0.4, 0.6)) 

```



