---
title: "Indicator 28"
author: "Destan Aytekin"
date: '2022-05-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Prepare the libraries
library(dplyr)
library(tidyr)
library(ggplot2)

```

##Including Plots for the dataset merged with WOrld Bank classifications and retitled as "data_indicator28_final1"

##20 observations were lost when data was merged with the WB classifications, as those data were not among the WB country list.

##2016-2018 data is used as it was most the recent year of data with good country coverage.

You can also embed plots, for example:

```{r pressure, echo=FALSE}

##Changing WBIncome into WBRegion would generate the boxplot for World Bank Regions.

data_indicator28_final1 %>% ggplot(aes(WBIncome,Percentage)) + ylab('Share of dietary energy from roots cereals tubers') + geom_boxplot() + geom_point()


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
